% Indicate the main file. Must go at the beginning of the file.
% !TEX root = ../main.tex
%----------------------------------------------------------------------------------------
% CHAPTER 2
%----------------------------------------------------------------------------------------

\chapter{Current State of the Art}

\label{Chapter2} % For referencing the chapter elsewhere, use \ref{Chapter2} 

%----------------------------------------------------------------------------------------
As Humble and Molesky \cite{HumbleMolesky2011} point out that the four most fundamental aspects are culture, automation, measurement and knowledge sharing we are going into what these different aspects are in depth and how they can help us to tackle the evolving ecosystem. \ac{DevOps} has increased the speed of the deployment and management of products as mentioned from Zhu \cite{Zhu2016DevOps}, this also introduces new challenges. In \cite{Zhu2016DevOps} Zhu is writing about the cultural and technical aspects, which are associated within the transformation of a organization.

However, Jabbari \cite{Jabbari2016} notes in his paper that \ac{DevOps} is not merely about tools and processes - it is also about fostering a culture that enhances communication and collaboration among all stakeholders involved in software development and delivery. Current definitions focus on development and operations, but future iterations may include a broader integration with business operations. This would make \ac{DevOps} a central part of business strategy rather than just a software development methodology.

The term "\ac{DevOps}" is open to a range of interpretations, encompassing toolchains, cultural practices, job titles, and responsibilities. Humble and Molesky identified four fundamental pillars of \ac{DevOps}, as outlined in their paper \cite{HumbleMolesky2011}.

\begin{itemize}
    \item \textbf{Culture:} the sharing of responsibility for the delivery of software
    \item \textbf{Automation:} automation is a useful tool for increasing the efficiency of processes
    \item \textbf{Measurement:} the quantification of processes helps to understand capability and to set goals
    \item \textbf{Knowledge Sharing:} the most crucial aspect of knowledge sharing is the method of sharing
\end{itemize}


Of these, Knowledge Sharing is of central importance as it underpins the effective adoption of \ac{DevOps} practices and facilitates knowledge management in the organization
\cite{Azad2023DevOps} .

\section{Culture}

The results presented in by Hermawan \cite{Hermawan2021DevOpsTeamwork} demonstrate that the integration of \ac{DevOps} practices significantly enhances teamwork quality. The fostering of a collaborative culture, characterised by the encouragement of knowledge sharing and efficient teamwork, is a key identifier of \ac{DevOps}. The continuous improvement and feedback cycles inherent to \ac{DevOps} engage all team members in the iterative processes of development, leading to increased accountability and a more dynamic work environment. The implementation of the \ac{DevOps} methodology ensures that team members provide mutual support and respect each other’s contributions, thereby facilitating collaboration in the effective management of challenges, ultimately leading to a more productive and harmonious work environment.

As previously noted by Mazur \cite{Mazur2023}, effective leadership is crucial in establishing and maintaining quality expectations within an organisation. By emphasising quality and demonstrating commitment to this goal, leaders can create an environment where employees are motivated to adhere to those standards, which subsequently enhances team collaboration and product outcomes. Implementing continuous improvement mechanisms and providing regular feedback within teams can facilitate improvements in working practices and product quality. Furthermore, teams that adopt a learning-oriented approach, where members engage in collective adaptation and knowledge sharing, tend to develop a stronger collaborative culture.

Furthermore, De Church and colleagues' research \cite{Dechurch2010} indicates that collaboration and effective communication between team members are significant factors in an organisation's success. It suggests that the benefits of team cognition vary depending on team and task characteristics. For example, highly interdependent teams may gain more from well-developed transactive memory systems than less interdependent teams. The research also highlights the importance of shared mental understandings in team effectiveness. These models assist team members in developing compatible understandings of their tasks and environment, thereby facilitating coordinated and efficient task performance. The study further indicates that transactive memory systems, which entail a shared understanding of which team members possess specific information, are vital for effective information processing and utilisation within teams. The findings indicate that the benefits of team cognition vary according to team and task characteristics.

Pinto \cite{Pinto1990} defines the quality of communication within a team as the frequency and formalisation of the information exchange between team members. The frequency is determined by the frequency with which communication occurs among team members and the time spent on it. Formalisation refers to the degrees of spontaneity in the communication. Communication that requires significant planning and includes written status reports is considered formal, while spontaneous communication, such as talking in the doorway, chatting, or talking in front of a screen, is considered informal. It can be observed that ideas and contributions are typically shared, discussed, and evaluated with other team members in a timelier and more efficient manner through informal communication than formal communication. 


\section{Automation}

The article \cite{McBurney2017PrioritizingDocEffort} outlines the potential of automation in the prioritization process of documentation efforts. This suggests that automation can assist in determining which sections of code require the most detailed documentation, thus optimizing the use of limited time and resources. The research findings indicate that textual analysis of source code, using techniques like \ac{VSM} and textual comparison, is effective in predicting documentation priorities. This implies that the implementation of artificial neural networks to automate the prioritisation process demonstrates the potential of machine learning technologies to enhance the efficiency and accuracy of determining documentation needs, with the capability of handling large codebases.

In his paper, Procko \cite{Procko2024CodeDocumentation} demonstrates the efficiency of automation through integration with Git repositories for real-time generation of code documentation. This eliminates the need for manual updates, significantly speeding up the documentation process. Procko's work also addresses the issue of \textit{documentation debt} – a situation whereby changes made to code are not reflected in its documentation. The automation of the documentation process ensures that the documentation remains consistent with the code, thereby reducing the likelihood of outdated information. Furthermore, the integration of the \ac{ACDC} system into \ac{CI} and \ac{CD} pipelines demonstrates the potential for automation to streamline software development processes. This integration helps to ensure that documentation is maintained without requiring additional effort from developers, thus allowing them to focus their attention on coding tasks rather than on documentation. The utilisation of \ac{GPT} and \ac{AST} in the \ac{ACDC} system exemplifies the role of advanced technologies in automating complex tasks. These technologies facilitate the generation of accurate, context-sensitive documentation in an automated manner. By automating the documentation generation process, the \ac{ACDC} system allows developers to allocate more time and resources to other crucial aspects of software development, thereby enhancing overall productivity.
 

\section{Measurement}

Manuel Sánchez Ruiz \cite{Ruiz2023}, suggests that measuring aspects such as release frequency and lead time for changes enables teams to gauge their efficiency and productivity. The release frequency is utilized to assess how often a team successfully updates their project, which can be a direct indicator of the team’s ability to work effectively together and push updates regularly. The assessment of the lead time for changes allows the identification of the interval between code commit and code release. A reduction of this period may indicate the existence of a collaborative environment, characterised by the rapid development and deployment of changes. Conversely, a prolonged lead time may suggest a less efficient and collaborative team dynamic, where issues are not addressed promptly, thus affecting productivity and the health of the project.

Furthermore, Floris Erich \cite{Erich2017DevOps} notes that measurement is closely tied to performance improvements in \ac{DevOps} practices. By measuring key performance indicators, organisations can better understand the contributions of team collaboration to overall productivity and quality of software delivery. However, aligning measurement practices with the dynamic and integrated nature of \ac{DevOps} teams can be complex. Effective measurement strategies are therefore needed to accurately capture the nuances of collaboration within \ac{DevOps} teams. The measurement of the frequency and effectiveness of interactions between team members can provide insights into the efficacy with which teams collaborate in the achievement of shared objectives.


\section{Knowledge Sharing}


The value of knowledge sharing in solving complex problems more effectively is emphasised by Crosby in his book \cite{Crosby2023}, where he cites a number of examples to illustrate his points. By sharing diverse expertise and perspectives, teams can develop more comprehensive solutions that consider multiple aspects of a problem. Furthermore, knowledge sharing helps in standardising best practices across teams. This standardisation leads to more consistent and efficient processes, since team members are more likely to adopt proven methods rather than reinventing the wheel. Knowledge sharing among team members expedites the onboarding process for newcomers, while simultaneously aiding the advancement of skills amongst existing members. The continuous learning environment that ensues encourages a culture of continuous improvement and adaptability. With a shared knowledge base, team members have access to a broader array of information, which can lead to more informed decision-making. This is particularly pertinent in dynamic environments where decisions need to be made swiftly and efficiently. The breakdown of information silos, which knowledge sharing facilitates, enables a more collaborative and integrated team environment. This integration serves to align the team's efforts towards a unified goal, thereby enhancing overall team performance.


As evidenced by Kuusinen \cite{Kuusinen2017} in her survey of the subject, the results demonstrate that the application of more agile techniques is correlated with increased ease of sharing knowledge among team members. Agile environments facilitate open communication and continuous feedback, both of which are essential for effective collaboration in the resolution of problems. However, while the implementation of agile methods has been demonstrated to significantly enhance the sharing of knowledge within teams, they have not proven to be as efficacious in facilitating knowledge transfer between teams or across organisational boundaries. These results imply the necessity for organisational strategies to promote the dissemination of knowledge beyond the immediate team environment. The study highlights the distinction in motivation between knowledge sharing within teams and knowledge sharing with external parties (colleagues within the organisation or customers). Within teams, intrinsic motivations (e.g. enjoyment of collaborative work) prevail, whereas extrinsic factors (e.g. building customer relationships) play a more significant role in interactions with external stakeholders. An understanding of these motivational nuances can assist in the development of tailored approaches to improve knowledge sharing practices in a more effective manner. The survey indicated that informal communication methods, such as casual discussions and the use of whiteboard technology, were more effective for the sharing of knowledge within teams than formal methods, including presentations and emailing. This emphasises the significance of enriching an environment that encourages spontaneous and informal interactions among those who work together. The study indicates that the sharing of knowledge beyond the immediate team remains challenging, primarily as a consequence of a lack of organisational support and the absence of appropriate incentives. The development of a culture that values the sharing of knowledge throughout the organisation is of critical importance to the improvement of collaboration and efficiency on a larger scale.


\section{Conclusion}

This chapter provides a comprehensive analysis of the state of the art in \ac{DevOps} practices. It emphasises the critical aspects of culture, automation, measurement, and knowledge sharing. As outlined by Humble and Molesky \cite{HumbleMolesky2011}, these four pillars form the foundation upon which effective \ac{DevOps} practices are built.

It is evident that the integration of \ac{DevOps} has a positive impact on teamwork, as well as fostering a collaborative culture, which can be evidenced by Hermawan’s \cite{Hermawan2021DevOpsTeamwork} work. It is also clear that effective leadership, coupled with continuous improvement mechanisms, is vital in maintaining high quality and fostering a learning-oriented environment, as highlighted in Mazur’s \cite{Mazur2023} and De Church’s \cite{Dechurch2010} research.

Automation is a key factor in streamlining processes and reducing manual efforts, as evidenced by McBurney \cite{McBurney2017PrioritizingDocEffort} and Procko \cite{Procko2024CodeDocumentation}. By leveraging advanced technologies such as artificial neural networks and integrating automation into \ac{CI}/\ac{CD} pipelines, organisations can significantly enhance their productivity and maintain up-to-date documentation.

The measurement of efficiency and productivity in \ac{DevOps} teams represents an indispensable aspect. This is evidenced by the contributions of Ruiz \cite{Ruiz2023} and Erich \cite{Erich2017DevOps}, who highlight the importance of key performance indicators such as release frequency and lead time for changes. In order to capture the nuances of team collaboration and drive performance improvements, effective measurement strategies are needed.

Finally, it can be demonstrated that knowledge sharing is of paramount importance for the solution of complex problems, the standardisation of best practices and the fostering of continuous improvement. In their respective works, Crosby \cite{Crosby2023} and Kuusinen \cite{Kuusinen2017} have discussed how the utilisation of agile environments facilitates open communication and continuous feedback. However, challenges remain in the dissemination of knowledge beyond immediate teams. It is therefore of the utmost importance to develop organisational strategies which promote the sharing of knowledge on a broader scale, with the objective of enhancing overall collaboration and efficiency.

In conclusion, the integration of culture, automation, measurement, and knowledge sharing into the context of \ac{DevOps} practices leads to a more efficient, collaborative, and dynamic work environment. Future research and practical implementations should continue to focus on these pillars in order to enhance \ac{DevOps} methodologies and their contributions to organisational success.
